Pulling oral and IV data from CvTdb

### 2022-12-15 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Normalize LOQ units to mg/L.

Filter down to only blood/plasma studies and to only oral/iv administration.

```{r}
cvt_data <- cvt_data[series.conc_medium_normalized %in% c("blood", "plasma") &
                       studies.administration_route_normalized %in% c("oral", "iv")]
```

@@

```{r}
tmp <- cvt_data[chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187"]
```

@@

>>>>

@@

```{r}
tmp <- cvt_data[chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187" &
                  studies.administration_route_normalized %in% c("oral", "iv") &
                  series.conc_medium_normalized %in% c("blood", "plasma")]
```

@@

# Normalize LOQ units to mg/L

```{r}
cvt_data[, unique(series.loq_units)]
```

```{r}
cvt_data[, series.loq := as.numeric(series.loq)]
cvt_data[series.loq_units %in% "ug/L", series.loq_normalized := series.loq * 1e-3]
cvt_data[trimws(series.loq_units) %in% "ug/mL", series.loq_normalized := series.loq]
cvt_data[series.loq_units %in% "mg/L", series.loq_normalized := series.loq]
cvt_data[series.loq_units %in% "ng/mL", series.loq_normalized := series.loq * 1e-3]
```

For that with nmol/L we will need the molecular weight. For items with units ug we would need the volume of media analyzed. Both of these are for inhalation data, though, which we are not analyzing right now. So I will leave it alone for now.
